---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fractionalBM

<!-- badges: start -->
<!-- badges: end -->

The goal of fractionalBM is to provide several different ways of simulating discrete paths of fractional Brownian Motion for different lengths of time, and different Hurst parameters. 

## Installation

You can install the released version of fractionalBM from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fractionalBM")
```

## Sample plots

This is a basic example which shows you how to generate paths of fractional Brownian motion:

```{r example}
library(fractionalBM)

h02 = FBM(1000, 0.2)
h05 = FBM(1000, 0.5)
h08 = FBM(1000, 0.8)

plot(h02,type='l')
title(main='Hurst = 0.2')

plot(h05, type='l')
title(main='Hurst = 0.5')

plot(h08, type='l')
title(main="Hurst = 0.8")

```

